%-------------------------
% Resume in Latex
% Author : Runit Misra
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\fourSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Runit Misra} \\ \vspace{1pt}
    \small +91 9512229449 $|$ \href{mailto:misra.runit@gmail.com}{\underline{misra.runit@gmail.com}} $|$ 
    \href{https://linkedin.com/in/runit-misra}{\underline{linkedin.com/in/runit-misra}} $|$
    \href{https://github.com/runitmisra}{\underline{github.com/runitmisra}} $|$
    \href{https://www.runitmisra.in}{\underline{runitmisra.in}}
\end{center}

%
%-----------SUMMARY-----------
\section{Professional Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Cloud Native enthusiast with \textbf{5 years of experience} as a Site Reliability Engineer, specializing in observability, reliability, and scalability of complex systems. \textbf{Certified Kubernetes Administrator} skilled in developing robust cloud infrastructure, orchestrating application deployments on Kubernetes, and implementing Infrastructure as Code (IaC). Proficient in automation, monitoring, and continuous integration/continuous deployment (CI/CD) pipelines. Highly motivated engineer with strong problem-solving and communication skills and experience in learning and growing in a fast-paced environment.}}
 \end{itemize}

%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Cloud Providers}{: AWS, GCP} \\
     \textbf{Containerization}{: Docker} \\
     \textbf{Orchestration}{: Kubernetes, Argo} \\
     \textbf{CI/CD}{: Github Actions, Gitlab CI, Argo CD} \\
     \textbf{Kubernetes Tools}{: Helm, Rancher, Rook Ceph, Kubernetes Operators} \\
     \textbf{Monitoring Tools}{: Prometheus, Grafana, Loki, Elasticsearch(ELK), Kibana, Fluent-bit, Splunk} \\
     \textbf{Infrastructure as Code}{: Terraform} \\
     \textbf{Programming Languages}{: Golang(Go), Python, Shell Scripting} \\
     \textbf{Operating Systems}{: Linux}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \fourSubheading
      {Certified Kubernetes Administrator}{January 2023}
      {LF-xnjmimklor}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Site Reliability Engineer - InfraCloud Technologies}{October 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Lead DevOps/SRE for blockchain-based projects at one of India's largest FinTech companies, acting as the sole contributor and SME for on-prem and GCP Kubernetes infrastructure design, support and troubleshooting.}
        \resumeItem{Designed and implemented a highly available, multi-site, active-active Hyperledger Fabric deployment on air-gapped on-premises Rancher Kubernetes(RKE) clusters, handling a high transaction throughput of approximately 250 TPS.}
        \resumeItem{Developed Gitlab CI pipeline for building Go and Java application docker images in an air-gapped environment.}
        \resumeItem{Utilized SNI-based routing with CoreDNS, Nginx Ingress Controller and HAProxy to route traffic between multiple physical data centers across India, enabling a single Hyperledger Fabric cluster formation.}
        \resumeItem{Managed monitoring and incident response for production Kubernetes clusters using Prometheus and Grafana for metrics, and Elasticsearch, Fluent-bit, and Kibana for log shipping and aggregation.}
        \resumeItem{Contributed to the open-source project Falcon (https://github.com/npci/falcon), a Helm-based deployment helper for Hyperledger Fabric on Kubernetes. Added Prometheus monitoring support to Helm charts and implemented general fixes.}
      \resumeItemListEnd

    \resumeSubheading
      {Associate Site Reliability Engineer - InfraCloud Technologies}{July 2021 -- October 2022}
      \resumeItemListStart
        \resumeItem{Contributed to Fission open source project, a fast serverless framework for kubernetes (https://github.com/fission/fission) by enhancing developer experience and providing general fixes.}
        \resumeItem{Helped Fission Enterprise customers by providing SRE and Cloud expertise to help right-size and scale their Fission Enterprise deployments}
        \resumeItem{Created Terraform EKS wrapper module on top of AWS upstream module with opinionated defaults and following best practices for company-wide usage.}
        \resumeItem{Contributed in planning and system design of a SaaS cloud security platform on AWS using Terraform, Kubernetes and GitOps principles from scratch.}
        \resumeItem{Designed and implemented fully automated Github Actions CI pipeline to run unit tests, linters, build application images and upload artifacts for multiple environments.}
        \resumeItem{Designed GitOps CD pipeline using ArgoCD using advanced Gitops patters like app-for-apps, enabling seamless application deployment to kubernetes with no manual intervention.}
        \resumeItem{Created an automated and platform agnostic Datadog monitoring system using Terraform for several customer applications for log aggregation, metrics, APM and RUM.}
        \resumeItem{Onboarded 10+ applications to Datadog running on different platforms like Bare Metal, Serverless, Kubernetes, GCP, AWS, Azure and OSes like Linux and Windows.}
        \resumeItem{Used Terraform to automate the process of creating Alerts and Dashboards with the help of the DataDog Terraform provider.}
     \resumeItemListEnd
    \resumeSubheading
      {Site Reliability Engineer - Crest Data Systems}{May 2019 -- July 2021}
      \resumeItemListStart
        \resumeItem{Worked on Splunk Cloud SaaS platform among an international team of SREs, NOC engineers, Change Managers and Product Developers for 5000+ customers including many Fortune 500 companies.}
        \resumeItem{Provided AWS Infrastructure and Splunk cloud support using Terraform and Puppet to keep mission critical customer infrastructure running securely on PCI DSS and HIPAA compliant networks.}
        \resumeItem{Followed strict change management processes by following, updating and creating operational runbooks, working on JIRA issues related to customer change requests and troubleshooting customer issues.}
        \resumeItem{Trained 5+ newly joined SREs in Splunk CloudOps processes and practices.}
      \resumeItemListEnd
    

    \resumeSubheading
      {Project Management Intern - Crest Data Systems}{December 2018 -- May 2019}
      \resumeItemListStart
        \resumeItem{Ensured proper Agile process compliance across 4 projects}
        \resumeItem{Held daily Scrum meetings, Managed JIRA boards, Created reports like velocity charts and burn-down charts}
        \resumeItem{Exposed to several practices in a project’s life cycle from Sprint Planning to Delivery}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \fourSubheading
      {Charotar University of Science and Technology}{}
      {Bachelor of Techology in Computer Engineering}{July 2015 -- May 2019}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
